### 2013-04-08 inst/examples/Reed.Rmd
add value iteration termination to package functions, example shown in Reed.md

``` {r  echo=FALSE, cache=FALSE}
#opts_knit$set(upload.fun = socialR::flickr.url)
#options(device = function(width = 5, height = 5) {
#    pdf(NULL, width = width, height = height)
#})
knitcitations::cleanbib()
````

@@

``` {r }
f <- function (x, h, p) 
{
 sapply(x, function(x){
  	S = max(x - h, 0)
  	p[1] * S * (1 - S/p[2]) + S
  })
}

````

With parameters `K` = `r K <- 100` and `r` = `r r <- 1`.

``` {r }
pars <- c(r, K)
````

@@

@@

``` {r policyfn_plot}
require(reshape2)
policies <- melt(data.frame(stock=x_grid, S = x_grid[opt$D[,1]], D = x_grid[det$D[,1]]), id="stock")
q1 <- ggplot(policies, aes(stock, stock - value, color=variable)) + geom_point() + xlab("stock size") + ylab("escapement") 
q1
````

>>>>

``` {r  echo=FALSE, cache=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
````

@@

``` {r }
f <- function (x, h, p) 
{
 sapply(x, function(x){
  	S = max(x - h, 0)
  	p[1] * S * (1 - S/p[2]) + S
  })
}
````

``` {r }
r <- 1
K <- 100
pars <- c(r, K)
````

With parameters `K` = `r K` and `r` = `r r`.

@@

Stationary optimal policy:

``` {r value_iteration }
s_opt <- value_iteration(SDP_Mat, x_grid, h_grid, OptTime=1000, xT, profit, delta)
````

@@

``` {r policyfn_plot}
require(reshape2)
policies <- melt(data.frame(stock=x_grid, S = x_grid[opt$D[,1]], D = x_grid[det$D[,1]], Stationary = x_grid[s_opt$D]), id="stock")
q1 <- ggplot(policies, aes(stock, stock - value, color=variable)) + geom_point(alpha=.5) + xlab("stock size") + ylab("escapement") 
q1
````
